### 2025-04-22 paper/ecai2025/appendices/arch.tex
first pass on spacing

\begin{figure}[t]
    \centering
    \includegraphics[width=.45\textwidth]{figs/attention.pdf} 
    \caption{Attention matrix for the world model.}
    \label{apx:fig:attention}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=.45\textwidth]{figs/grads-mlp-transport.pdf}
    \caption{Gradient norm for a transformer architecture wrt. a MLP architecture.}
    \label{fig:grads-mlp}
\end{figure}

@@

As mentioned earlier, we test PPO, SHAC, \fname{}, and \fnamer{} with two different architecture---Transformer and MLP. The former is a popular positional invariant architecture for sequence modeling~\cite{Vaswani17}. While the latter is a simple feed-forward neural network.

>>>>

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=.45\textwidth]{figs/attention.pdf} 
    \caption{Attention matrix for the world model.}\vspace{0.5cm}
    \label{apx:fig:attention}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=.45\textwidth]{figs/grads-mlp-transport.pdf}
    \caption{Gradient norm for a transformer architecture wrt. a MLP architecture.}\vspace{0.5cm}
    \label{fig:grads-mlp}
\end{figure}
As mentioned earlier, we test PPO, SHAC, \fname{}, and \fnamer{} with two different architecture---Transformer and MLP. The former is a popular positional invariant architecture for sequence modeling~\cite{Vaswani17}. While the latter is a simple feed-forward neural network.

### 2025-04-22 paper/ecai2025/appendices/scenarios.tex
first pass on spacing

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{0.24\textwidth}
        \includegraphics[width=\textwidth]{figs/dispersion.png}
        \caption{Dispersion}
        \label{fig:dispersion}
    \end{subfigure}
    \begin{subfigure}[b]{0.24\textwidth}
        \includegraphics[width=\textwidth]{figs/transport.png}
        \caption{Transport}
        \label{fig:transport}
    \end{subfigure}
    \begin{subfigure}[b]{0.24\textwidth}
        \includegraphics[width=\textwidth]{figs/discovery.png}
        \caption{Discovery}
        \label{fig:discovery}
    \end{subfigure}
    \begin{subfigure}[b]{0.24\textwidth}
        \includegraphics[width=\textwidth]{figs/sampling.png}
        \caption{Sampling}
        \label{fig:sampling}
    \end{subfigure}
    \caption{VMAS environments used in the experiments.}\label{fig:scenarios}
\end{figure}

\section{Environments}\label{apx:scenarios}

@@

\subsection{Dicsovery}
In the Discovery task, $n$ agents aim to collect as many randomly placed goals as possible. When they successfully collect $k$ goals, another $k$ goals are randomly placed. To collect a goal, at least $s$ agents must be in proximity to it. In \Cref{fig:discovery}, the agents are represented by blue dots, while the goals are depicted as green dots. The proximity area is indicated by a dashed circle. In our experiments, we set $s=2$ and $k=7$ when $n > 1$. When $n = 1$, we set $s=1$ and $k=7$.

>>>>

\section{Environments}\label{apx:scenarios}
\begin{figure}
    \centering
    \begin{subfigure}{0.24\textwidth}
        \includegraphics[width=\textwidth]{figs/dispersion.png}
        \caption{Dispersion}
        \label{fig:dispersion}
    \end{subfigure}
    \begin{subfigure}{0.24\textwidth}
        \includegraphics[width=\textwidth]{figs/transport.png}
        \caption{Transport}
        \label{fig:transport}
    \end{subfigure}
    \begin{subfigure}{0.24\textwidth}
        \includegraphics[width=\textwidth]{figs/discovery.png}
        \caption{Discovery}
        \label{fig:discovery}
    \end{subfigure}
    \begin{subfigure}{0.24\textwidth}
        \includegraphics[width=\textwidth]{figs/sampling.png}
        \caption{Sampling}
        \label{fig:sampling}
    \end{subfigure}
    \caption{VMAS environments used in the experiments.}\label{fig:scenarios}\vspace{0.5cm}
\end{figure}

@@

\subsection{Discovery}
In the Discovery task, $n$ agents aim to collect as many randomly placed goals as possible. When they successfully collect $k$ goals, another $k$ goals are randomly placed. To collect a goal, at least $s$ agents must be in proximity to it. In \Cref{fig:discovery}, the agents are represented by blue dots, while the goals are depicted as green dots. The proximity area is indicated by a dashed circle. In our experiments, we set $s=2$ and $k=7$ when $n > 1$. When $n = 1$, we set $s=1$ and $k=7$.
